\cvsection{Work Experience}
\begin{cventries}
\cventry
    {Staff Software Engineer} % Job title
    {Cruise, Kernels Optimization and Performance} % Organization
    {Seattle, Washington, USA} % Location
    {May '23 - Present} % Date
    {
        \begin{cvitems}
          \item Implemented and benchmarked optimized implementations of MLIR operators in OpenCL, CPU/Highway, and CUDA
          \item Collaborated on next-generation accelerator software strategy, performing experiments and working with Perception, Hardware, and Runtime teams to fit algorithms and ML models to our future accelerator designs
          \item Implemented Pytorch operator that wraps an elementwise function and executes it CUDA, CPU, or OpenCL, unblocking model deployment
          \item Worked with a third-party vendor to improve OpenCL code generation and expose hardware intrinsics, improving throughput over 30\%
          \item Implemented clangd code completion for CUDA, OpenCL, and DSP sources and collaborated with build team to deploy across Cruise
          \item Implemented proof-of-concept DSP toolchain in Bazel, and worked with vendor to enable DSP compilation in remote Bazel environment
        \end{cvitems}
    }
\vspace{4mm}
\cventry
    {Senior Software Engineer Team Lead/Manager (TL/M)} % Job title
    {Google, gChips Software Experiences} % Organization
    {Seattle, Washington, USA} % Location
    {Feb '22 - May '23} % Date
    {
        \begin{cvitems}
          \item Prototyped efficient camera algorithms accelerated across GPU, TPU, and DSP for Pixel 7 and future devices
          \item Performed silicon and simulation experiments to drive hardware requirements for future Pixel devices
          \item Developed OCLTrace - Tooling for linking GPU activity to detailed traces, to diagnose performance opportunities in OpenCL code
          \item Hired and managed a small team of engineers to investigate silicon requirements for future health use-cases
        \end{cvitems}
    }
\vspace{4mm}
\cventry
    {Software Development Engineer II} % Job title
    {Amazon.com, Robotics - Industrial Internet of Things (IIoT)} % Organization
    {Seattle, Washington, USA} % Location
    {May '19 - Feb '22} % Date
    {
        \begin{cvitems}
            \item Designed and implemented a DSP and GPU-accelerated image processing pipeline for mobile SoCs.
            \item Designed and implemented a serverless corporate device management solution using AWS IoT and Lambda.
            \item Designed and implemented Android OS modifications to expose custom hardware peripherals.
            \item Implemented a realtime projected-light augmented reality system for sortation use-cases.
            \item Mentored teammates and interns through work review and weekly 1-on-1s
        \end{cvitems}
    }
\vspace{4mm}
\cventry
    {Software Development Engineer I} % Job title
    {Amazon.com, Alexa for Business} % Organization
    {Seattle, Washington, USA} % Location
    {May '18 - May '19} % Date
    {
        \begin{cvitems}
            \item Designed and implemented Polycom video conferencing integration with Alexa for Business.
            \item Implemented Full-CD pipeline and policies for team, including testing requirements and automated deployments.
        \end{cvitems}
    }
\vspace{4mm}
\cventry
    {CAS Student Fellow / Co-op Software Developer} % Job title
    {IBM Canada, Compilers Group / Cloud Innovation Lab} % Organization
    {Toronto, Ontario, Canada} % Location
    {Dec. '15 - May '16, May '14 - June '15} % Date
    {
        \begin{cvitems}
            \item Implemented GPU data transfer for OpenMP 4.5 in the XL compiler.
            \item Prototyped and shipped novel GPU loop optimizations, speeding GPU execution by 25\%.
            \item Developed a functional programming language (IBM Dash) and compiler for GPU execution. Wrote language specifications, compiler optimizations, and language runtime extensions.
            \item Implemented automated testing and continuous deployment on projects across the team with GitLab and Jenkins.
        \end{cvitems}
    }
\iffalse
\vspace{4mm}
\cventry
    {Software Development Engineer Intern} % Job title
    {Amazon.com, Fulfillment Technologies} % Organization
    {Seattle, Washington, USA} % Location
    {Sept. '13 - Mar. '14,
    June '15 - Aug. '15} % Date
    {
        \begin{cvitems}
            \item Designed, implemented, and supported an Android chat application with Microsoft Lync integration.
            \item Designed and implemented bandwidth-aware security camera tablet application, monitoring thousands of warehouse cameras.
            \item Worked with a small (4-6) person team under an Agile continuous delivery process to support and update thousands of Android devices.
        \end{cvitems}
    }
\fi
\end{cventries}
